Paper without a name

### 2014-05-09 Article.tex
Changes.
Article.tex modifié

>>>>

\section{Conclusion}

All these results seem to confirm our intuition.
To go further, we unsuccessfully tried to find applications from the set of trees representing a sort by binary insertion to the set of valid configurations of boxes 
that would be either one to one or onto, in order to find an inequality between these two sequences of integers.
We also tried to put our construction of configurations in relation with binary insertion sort.
